Assigning Scouts to Optimal Patrols

### 2016-06-08 draft1.tex

For our problem, we can define a graph where scouts are vertices. A directed edge between Scout A and Scout B has a weight proportional to how much Scout A likes Scout B. We give the directed edge between scout A and scout B a weighting of 1 if A likes B, 0 if A is indifferent to B, and a -1 if A disapproves of B. This results in a complete, directed graph of 13 vertices, since there are 13 scouts. Note that these edges are directed; we want to consider cases where the relationship between two scouts is not symmetric, whereas a weighted undirected graph would not be able to represent this asymmetry. Let us now define a $k$-partition of a graph as a grouping of vertices where each vertex is assigned into one of $k$ groups where $k$ is a natural number; thus, a $k$-partition of the vertices in the scout graph would represent splitting up the scouts into $k$ different patrols. Scoutmaster Bruce specifically would like two patrols from the 13 scouts - one of size 6, the other of size 7, which means that we need to find a 2-partition of the graph where 6 vertices are in one grouping and 7 are in the other. The total number of partitions given these constraints is $\binom{13}{6} = \binom{13}{7} = 1716$. Given these 1716 partitions, we want to select one of them that is ``best" for the scouts in question. In mathematics, picking the ``best" option out of a list of options corresponds to first defining a function that ``scores" how good an item is (or bad an item is) and then picking the item with the highest score (or the least score, if our scoring function defines how bad an item is). This process of selecting the item from a list that has the most extreme score is called optimization. From now on, we will call these scoring functions objective functions. Our process for optimizing a partition of the scouts will become computing an objective function for each possible partition and then selecting the partition that gives us the most extreme score. This ``brute force" approach to computing the scores isn't always appropriate for optimizing an objective function over a set of values, as the size of the set of values is often too large for a computer to iterate over in a timely fashion. Often, a more sophisticated technique will be required to iterate over a manageable subset of the set of possible values. However, 1716 is within the range of sizes of sets to iterate over where we could apply a brute force technique to solve for the most optimal partition.

>>>>

For our problem, we can define a graph where scouts are vertices. A directed edge between Scout A and Scout B has a weight proportional to how much Scout A likes Scout B. We give the directed edge between scout A and scout B a weighting of 1 if A likes B, 0 if A is indifferent to B, and a -1 if A disapproves of B. This results in a complete, directed graph of 13 vertices, since there are 13 scouts. Note that these edges are directed; we want to consider cases where the relationship between two scouts is not symmetric, whereas a weighted undirected graph would not be able to represent this asymmetry. Let us now define a $k$-partition of a graph as a grouping of vertices where each vertex is assigned into one of $k$ groups where $k$ is a natural number; thus, a $k$-partition of the vertices in the scout graph would represent splitting up the scouts into $k$ different patrols. Scoutmaster Bruce specifically would like two patrols from the 13 scouts - one of size 6, the other of size 7, which means that we need to find a 2-partition of the graph where 6 vertices are in one grouping and 7 are in the other. The total number of partitions given these constraints is $\binom{13}{6} = \binom{13}{7} = 1716$ (see \textit{Appendix C}). Given these 1716 partitions, we want to select one of them that is ``best" for the scouts in question. In mathematics, picking the ``best" option out of a list of options corresponds to first defining a function that ``scores" how good an item is (or bad an item is) and then picking the item with the highest score (or the least score, if our scoring function defines how bad an item is). This process of selecting the item from a list that has the most extreme score is called optimization. From now on, we will call these scoring functions objective functions. Our process for optimizing a partition of the scouts will become computing an objective function for each possible partition and then selecting the partition that gives us the most extreme score. This ``brute force" approach to computing the scores isn't always appropriate for optimizing an objective function over a set of values, as the size of the set of values is too large for a computer to iterate over in a timely fashion. Often, a more sophisticated technique will be required to iterate over a manageable subset of the set of possible values. However, 1716 is within the range of sizes of sets to iterate over where we could apply a brute force technique to solve for the most optimal partition.
